Guarded Recursion in Agda via Sized Types

### 2019-02-01 code-oneclock-paper/latex/Introduction.tex
trying to cut

Dependent type theory is an expressive functional programming
language that underlies the deductive system of proof assistants such
as Coq, Agda, and Lean \cite{barras1997coq,de2015lean,norell}. It is a total language,
meaning that every program definable inside type theory is necessarily
terminating. This is an important requirement that ensures the
consistency of the type system.

>>>>

Dependent type theory is an expressive functional programming
language that underlies the deductive system of proof assistants such
as Agda and Coq \cite{norell,barras1997coq}. It is a total language,
meaning that every program definable inside type theory is necessarily
terminating. This is an important requirement that ensures the
consistency of the type system.
